Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-06 paper.tex
Added a section to describe iterations results

@@

From a practical standpoint, our study shows that reproducibility 
evaluations of the PreFreesurfer and Freesurfer pipelines can be 
conducted using only 50\% of the files produced by the evaluated 
pipelines, with an accuracy above 95\%. Potentially, this could reduce 
the computing time and storage required for such studies by a factor of 
2. However, such studies could not be conducted by processing only half 
of the subjects entirely, which would correspond to the Complete 
Columns sampling method. Instead, the processing of all the subjects 
should be initiated, and it should be terminated in a random uniform 
way, assuming that files are uniformly produced throughout the 
execution. On more complex matrices, such as the synthetic dataset 
studied here, the training ratio required to get a 95\% accuracy 
increases to 0.85 to 0.9.

>>>>

\subsection{Varying the number of iterations}
Figure~\ref{fig:iterations} illustrates the impact of the number of iterations used to minimizing the error of matrix factorization for the RFNU method and synthetic dataset with 50 factors. As it shown, the increase in the number of iterations have slight effect on the accuracy except in the low training ratio of 10\% where maximum 20 iterations deteriorates the accuracy by 20\% . Also in the high training ratio such as 80\% and 90\% where 2 iterations leads to lower accuracy.   
\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
\caption{Effect of the number of iterations used in ALS, RFNU method, 50 factors, synthetic dataset.}
\label{fig:iterations}
\end{figure}

@@

From a practical standpoint, our study shows that reproducibility 
evaluations of the PreFreesurfer and Freesurfer pipelines can be 
conducted using only 50\% of the files produced by the evaluated 
pipelines, with an accuracy above 95\%. Potentially, this could reduce 
the computing time and storage required for such studies by a factor of 
3 and iteration of 4. However, such studies could not be conducted by processing only half 
of the subjects entirely, which would correspond to the Complete 
Columns sampling method. Instead, the processing of all the subjects 
should be initiated, and it should be terminated in a random uniform 
way, assuming that files are uniformly produced throughout the 
execution. On more complex matrices, such as the synthetic dataset 
studied here, the training ratio required to get a 95\% accuracy 
increases to 0.85 to 0.9.
